Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-12-21 Manuscript_rev2-LL.tex
reinstating old version of Manuscript_rev2.tex

The estimate provided by the neural network can be improved further by
accounting for any prior information we know about the dimer. We
therefore, utilise Bayesian inference to update our neural networks
estimation.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer
$p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous
measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the
probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a
signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculation of error}
\label{sec:divergence}
Section~\ref{sec:Bayes} covered how Bayes theorem can be applied to estimate
the orientation of a dimer based on its scattering signal. To evaluate the estimation we can use the simulation in Section~\ref{sec:brownian}; we denote the dimer's \emph{actual} orientation as $\hat{\bf s}$ and use MSTM to calculate its light scattering $I(\hat{\bf s}, \theta)$. At each angle $\theta_k$ we use \eqref{eq:scale} to scale the measurements collected from our dimer and record them as $y_1(\hat{\bf s})$, $y_2(\hat{\bf s})$, $y_3(\hat{\bf s})$. These measurements signals are used to calculate $p(\hat{\bf n}_{\alpha}\parallel y_1, y_2, y_3)$, because we know $\hat{s}$ we can determine which reference orientation is closest, denoted as $\hat{\bf n}_{best}$.

>>>>

The estimate provided by the neural network can be improved further by
accounting for any prior information we know about the dimer. We
therefore, utilise Bayesian inference to update our neural networks
estimation.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of
our dimer $p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer
from previous measurement can be used to inform our estimate of
$p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The
latter prior $p(y)$ is the probability of measuring a signal
$(y_1, y_2, y_3)$.  This is given by taking the discrete integral over
collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From Eq.~\eqref{eq:bayes}, we get a mass probability distribution that
denotes the probability that our dimer is in orientation
$\hat{\bf n}_{\alpha}$ given a signal $(y_1, y_2, y_3)$.  In order to
evaluate the accuracy of our method, we tested it using a Brownian
dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Calculation of error
\label{sec:divergence}}

Section~\ref{sec:Bayes} covered how Bayes theorem can be applied to estimate
the orientation of a dimer based on its scattering signal. To evaluate the estimation we can use the simulation in Section~\ref{sec:brownian}; we denote the dimer's \emph{actual} orientation as $\hat{\bf s}$ and use MSTM to calculate its light scattering $I(\hat{\bf s}, \theta)$. At each angle $\theta_k$ we use \eqref{eq:scale} to scale the measurements collected from our dimer and record them as $y_1(\hat{\bf s})$, $y_2(\hat{\bf s})$, $y_3(\hat{\bf s})$. These measurements signals are used to calculate $p(\hat{\bf n}_{\alpha}\parallel y_1, y_2, y_3)$, because we know $\hat{s}$ we can determine which reference orientation is closest, denoted as $\hat{\bf n}_{best}$.
